Application Outline

### 2022-11-17 analysis/paper_draft3.Rmd
edits, updated caption to Figure 1; numbering of steps in Fig. 1

A _Batson_ challenge typically proceeds in a four-step sequence (Figure 1). First, the attorney must decide whether to challenge the opposing attorney's use of one or more peremptory strikes as based on illegal bias. Second, if challenged, the challenger must meet an initial burden (the _prima facie_ case) of producing just enough evidence of strike bias to raise a sufficient initial inference of illegal bias. Third, the striking attorney must proffer permissible reasons for their challenged strikes; and (4) the challenger must discredit those proffered reasons and ultimately persuade the trial judge that it is more likely than not that the striking attorney acted with illegal bias.

@@

```{r batsonworkflowfig, fig.cap="Inference from Historical Strike Data for  Batson Challenge", fig.align = 'center', out.width="100%", fig.pos = "h"}

@@

By their choice of $\alpha$, the lawyer explicitly and transparently denotes the degree of weight placed on the historical strike data in the analysis. This transparency thwarts lawyer efforts to strategically select $\alpha$ values to prove or disprove illegal strike bias. Rather, at the key steps of the _Batson_ challenge process (Figure \@ref(fig:batsonworkflowfig)), the lawyers on both sides of a _Batson_ challenge know that the lawyers on either side can always directly and repeatedly assess how sensitive any bias inference is to the choice of $\alpha$. In any case, the choice of $\alpha$ cannot always determine whether a trial judge finds illegal bias, because no approach to using historical strike data has that ability.

>>>>

A _Batson_ challenge typically proceeds in a four-step sequence (Figure 1). First, the attorney must decide whether to challenge the opposing attorney's use of one or more peremptory strikes as based on illegal bias. Second, if challenged, the challenger must meet an initial burden (the _prima facie_ case) of producing just enough evidence of strike bias to raise a sufficient initial inference of illegal bias. Third, the striking attorney must proffer permissible reasons for their challenged strikes. Fourth, the challenger must discredit those proffered reasons and ultimately persuade the trial judge that it is more likely than not that the striking attorney acted with illegal bias.

@@

```{r batsonworkflowfig, fig.cap="Inference from Historical Strike Data at Key Steps of Batson Challenge", fig.align = 'center', out.width="100%", fig.pos = "h"}

@@

By their choice of $\alpha$, the lawyer explicitly and transparently denotes the degree of weight placed on the historical strike data in the analysis. This transparency matters, because it thwarts lawyer efforts to strategically select $\alpha$ values to prove or disprove illegal strike bias. Rather, at the key steps of the _Batson_ challenge process (Figure \@ref(fig:batsonworkflowfig)), the lawyers on both sides of a _Batson_ challenge know that the lawyers on the other side can always directly and repeatedly assess how sensitive any bias inference is to the choice of $\alpha$. In any case, the choice of $\alpha$ cannot always determine whether a trial judge finds illegal bias, because no approach to inferring bias based on historical strike data has that ability.

### 2022-11-17 figures/batson_workflow_fig2.tex
changed label in figure from "historical data" to "past strikes"
edits, updated caption to Figure 1; numbering of steps in Fig. 1

\begin{tikzpicture}
  \node (A) at (0,0) [label=below:{argue \emph{Batson}},point,fill={blue}];	
  \node (B1) at (4,0) [label=below:{prima facie case},
                       point,fill={blue}];	
  \node (B2) at (8,0) [label=below:{proffer reasons},
                       point, fill={white}];
  \node (B3) at (12,0) [label=below:{prove bias},point,fill={blue}];
   \node (M) at (6,2) [state, drop shadow, fill={white}] {Model};
   \node (PB) at (6,1) [state] {bias estimate};
    \node (H) at (3,3) [state] {historical data};
    \node (C) at (9,3) [state] {current strikes};

>>>>

\begin{tikzpicture}
  \node (A) at (0,0) [label=below:{1. argue \emph{Batson}},point,fill={blue}];	
  \node (B1) at (4,0) [label=below:{2. prima facie case},
                       point,fill={blue}];	
  \node (B2) at (8,0) [label=below:{3. proffer reasons},
                       point, fill={white}];
  \node (B3) at (12,0) [label=below:{4. prove bias},point,fill={blue}];
   \node (M) at (6,2) [state, drop shadow, fill={white}] {Model};
   \node (PB) at (6,1) [state] {bias estimate};
    \node (H) at (3,3) [state] {past strikes};
    \node (C) at (9,3) [state] {current strikes};
